---
title: "OsPSYgeneFamily"
author: "Maya Ziebarth"
date: "2025-08-05"
output: 
  html_notebook: 
    toc: true
    css: www/reproductivestages.png
  html_document:
    theme: spacelab
    toc: yes
    toc_float: yes
runtime: shiny
---

```{r setup, include=FALSE, EVAL = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)

library(tidyverse)
library(jsonlite)
library(skimr)
library(dplyr)
library(janitor)
library(RColorBrewer)
library(paletteer)
library(ggthemes)
library(ggplot2)
library(shiny)
library(shinydashboard)
library(bslib)
library(shinythemes)
library(thematic)
library(rsconnect)
```

# Loading All Data and Converting 

## OsPSYR1	LOC_Os07g05740
### Main Stages 
```{r}
json_stringR1 <- '[{"name":"Seedling_Root_Rep1","value":"186.518"},{"name":"Seedling_Root_Rep2","value":"299.477"},{"name":"Seedling_Root_Rep3","value":"255.581"},{"name":"MatureLeaf_Rep1","value":"34.4201"},{"name":"MatureLeaf_Rep2","value":"8.15198"},{"name":"MatureLeaf_Rep3","value":"41.2431"},{"name":"YoungLeaf_Rep1","value":"61.7583"},{"name":"YoungLeaf_Rep2","value":"106.041"},{"name":"YoungLeaf_Rep3","value":"46.173"},{"name":"SAM_Rep1","value":"1371.08"},{"name":"SAM_Rep2","value":"1846.28"},{"name":"SAM_Rep3","value":"1374.58"},{"name":"YoungInflorescence_Rep1","value":"387.136"},{"name":"YoungInflorescence_Rep2","value":"339.229"},{"name":"YoungInflorescence_Rep3","value":"314.496"},{"name":"InflorescenceP2_Rep1","value":"190.025"},{"name":"InflorescenceP2_Rep2","value":"214.833"},{"name":"InflorescenceP2_Rep3","value":"218.335"},{"name":"InflorescenceP3_Rep1","value":"393.506"},{"name":"InflorescenceP3_Rep2","value":"370.559"},{"name":"InflorescenceP3_Rep3","value":"386.242"},{"name":"InflorescenceP4_Rep1","value":"305.965"},{"name":"InflorescenceP4_Rep2","value":"272.508"},{"name":"InflorescenceP4_Rep3","value":"306.641"},{"name":"InflorescenceP5_Rep1","value":"546.943"},{"name":"InflorescenceP5_Rep2","value":"498.505"},{"name":"InflorescenceP5_Rep3","value":"553.791"},{"name":"InflorescenceP6_Rep1","value":"122.77"},{"name":"InflorescenceP6_Rep2","value":"190.882"},{"name":"InflorescenceP6_Rep3","value":"148.922"},{"name":"Seed_S1_Rep1","value":"451.299"},{"name":"Seed_S1_Rep2","value":"738.009"},{"name":"Seed_S1_Rep3","value":"724.682"},{"name":"Seed_S2_Rep1","value":"131.774"},{"name":"Seed_S2_Rep2","value":"101.909"},{"name":"Seed_S2_Rep3","value":"175.655"},{"name":"Seed_S3_Rep1","value":"165.845"},{"name":"Seed_S3_Rep2","value":"113.435"},{"name":"Seed_S3_Rep3","value":"159.465"},{"name":"Seed_S4_Rep1","value":"113.005"},{"name":"Seed_S4_Rep2","value":"86.3515"},{"name":"Seed_S4_Rep3","value":"90.604"},{"name":"Seed_S5_Rep1","value":"122.226"},{"name":"Seed_S5_Rep2","value":"83.6413"},{"name":"Seed_S5_Rep3","value":"81.2791"},{"name":"Stigma_Rep1","value":"105.169"},{"name":"Stigma_Rep2","value":"117.937"},{"name":"Stigma_Rep3","value":"115.129"},{"name":"Ovary_Rep1","value":"398.195"},{"name":"Ovary_Rep2","value":"416.751"},{"name":"Ovary_Rep3","value":"337.358"},{"name":"SuspensionCell_Rep1","value":"194.988"},{"name":"Shoot_Rep1","value":"87.6737"},{"name":"Root_Rep1","value":"106.742"},{"name":"Anther_Rep1","value":"41.0533"},{"name":"Embryo_Rep1","value":"361.636"},{"name":"Endosperm_Rep1","value":"9.93091"},{"name":"5d-seed_Rep1","value":"109.226"}, {"name":"Aerobic_coleoptile_Rep1","value":"176.223"},{"name":"Aerobic_coleoptile_Rep2","value":"119.402"},{"name":"Anoxic_coleoptile_Rep1","value":"279.939"},{"name":"Anoxic_coleoptile_Rep2","value":"213.459"}, {"name":"RICE_CTRL","value":"115.129"}]'
ospsyr1JSON <- fromJSON(json_stringR1)
```

```{r}
OsPSYR1 <- ospsyr1JSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSYR1$value <- as.numeric(OsPSYR1$value)
```


### Leaf 
```{r}
json_stringR1L <- '[{"name":"R1","value":"1.90671"},{"name":"RICE_CTRL","value":"0.647706"},{"name":"R2","value":"2.12788"},{"name":"R3","value":"0.908569"},{"name":"R4","value":"0.944498"},{"name":"R5","value":"0.341341"},{"name":"R6","value":"0.16714"},{"name":"R7","value":"0.143236"},{"name":"R8","value":"0.154641"},{"name":"R9","value":"0.131562"},{"name":"R10","value":"0.10658"},{"name":"R11","value":"0.192609"}]'
OsPSYR1leaf <- fromJSON(json_stringR1L)

OsPSYR1leaf$value <- as.numeric(OsPSYR1leaf$value)
```


### Root
```{r}
json_stringR1R <- '[{"name":"EN_1","value":"0"},{"name":"EN_2","value":"0"},{"name":"EN_3","value":"0"},{"name":"Med_CTRL","value":"0"},{"name":"X35S_1","value":"0"},{"name":"X35S_2","value":"0"},{"name":"X35S_3","value":"0"},{"name":"MZ_1","value":"0"},{"name":"MZ_2","value":"0"},{"name":"MZ_3","value":"0"},{"name":"V_1","value":"0"},{"name":"V_2","value":"0"},{"name":"V_3","value":"0"},{"name":"MCO_1A","value":"0"},{"name":"MCO_1B","value":"0.657433"},{"name":"MCO_2A","value":"0"},{"name":"MCO_2B","value":"0"}]'
ospsyr1rootJSON <- fromJSON(json_stringR1R)
```

```{r}
OsPSYR1root <- ospsyr1rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSYR1root$value <- as.numeric(OsPSYR1root$value)
```



## OsPSYR2	LOC_Os04g42700
### Main Stages 
```{r}
json_stringR2 <- '[{"name":"Seedling_Root_Rep1","value":"1691.76"},{"name":"Seedling_Root_Rep2","value":"1613.14"},{"name":"Seedling_Root_Rep3","value":"1472.27"},{"name":"MatureLeaf_Rep1","value":"241.107"},{"name":"MatureLeaf_Rep2","value":"267.32"},{"name":"MatureLeaf_Rep3","value":"574.511"},{"name":"YoungLeaf_Rep1","value":"928.539"},{"name":"YoungLeaf_Rep2","value":"956.677"},{"name":"YoungLeaf_Rep3","value":"894.605"},{"name":"SAM_Rep1","value":"999.701"},{"name":"SAM_Rep2","value":"975.001"},{"name":"SAM_Rep3","value":"857.725"},{"name":"YoungInflorescence_Rep1","value":"4020.89"},{"name":"YoungInflorescence_Rep2","value":"2410.54"},{"name":"YoungInflorescence_Rep3","value":"2858.52"},{"name":"InflorescenceP2_Rep1","value":"2137.13"},{"name":"InflorescenceP2_Rep2","value":"2267.71"},{"name":"InflorescenceP2_Rep3","value":"2276.46"},{"name":"InflorescenceP3_Rep1","value":"4046.53"},{"name":"InflorescenceP3_Rep2","value":"3618.31"},{"name":"InflorescenceP3_Rep3","value":"4421.7"},{"name":"InflorescenceP4_Rep1","value":"4433.8"},{"name":"InflorescenceP4_Rep2","value":"4145.5"},{"name":"InflorescenceP4_Rep3","value":"4889.35"},{"name":"InflorescenceP5_Rep1","value":"2523.14"},{"name":"InflorescenceP5_Rep2","value":"2429.34"},{"name":"InflorescenceP5_Rep3","value":"2282.03"},{"name":"InflorescenceP6_Rep1","value":"1733.76"},{"name":"InflorescenceP6_Rep2","value":"1823.38"},{"name":"InflorescenceP6_Rep3","value":"1736.75"},{"name":"Seed_S1_Rep1","value":"2381.32"},{"name":"Seed_S1_Rep2","value":"2697.48"},{"name":"Seed_S1_Rep3","value":"2712.98"},{"name":"Seed_S2_Rep1","value":"2037.99"},{"name":"Seed_S2_Rep2","value":"1696.04"},{"name":"Seed_S2_Rep3","value":"2037.93"},{"name":"Seed_S3_Rep1","value":"1262.18"},{"name":"Seed_S3_Rep2","value":"1408.55"},{"name":"Seed_S3_Rep3","value":"1731.29"},{"name":"Seed_S4_Rep1","value":"1036.33"},{"name":"Seed_S4_Rep2","value":"904.301"},{"name":"Seed_S4_Rep3","value":"1113.98"},{"name":"Seed_S5_Rep1","value":"712.078"},{"name":"Seed_S5_Rep2","value":"766.468"},{"name":"Seed_S5_Rep3","value":"697.543"},{"name":"Stigma_Rep1","value":"1738"},{"name":"Stigma_Rep2","value":"1634.51"},{"name":"Stigma_Rep3","value":"1553.69"},{"name":"Ovary_Rep1","value":"1246.51"},{"name":"Ovary_Rep2","value":"1279.12"},{"name":"Ovary_Rep3","value":"1246.23"},{"name":"SuspensionCell_Rep1","value":"846.182"},{"name":"Shoot_Rep1","value":"363.016"},{"name":"Root_Rep1","value":"1197.82"},{"name":"Anther_Rep1","value":"413.025"},{"name":"Embryo_Rep1","value":"900.979"},{"name":"Endosperm_Rep1","value":"265.912"},{"name":"5d-seed_Rep1","value":"287.304"}, {"name":"Aerobic_coleoptile_Rep1","value":"1448.79"},{"name":"Aerobic_coleoptile_Rep2","value":"1283.9"},{"name":"Anoxic_coleoptile_Rep1","value":"789.858"},{"name":"Anoxic_coleoptile_Rep2","value":"857.482"}, {"name":"RICE_CTRL","value":"1070.69"}]'
ospsyr2JSON <- fromJSON(json_stringR2)
```

```{r}
OsPSYR2 <- ospsyr2JSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSYR2$value <- as.numeric(OsPSYR2$value)
```

### Leaf 
```{r}
json_stringR2L <- '[{"name":"R1","value":"1.45633"},{"name":"RICE_CTRL","value":"0.627036"},{"name":"R2","value":"1.49258"},{"name":"R3","value":"0.718278"},{"name":"R4","value":"0.891138"},{"name":"R5","value":"0.34235"},{"name":"R6","value":"0.261122"},{"name":"R7","value":"0.206563"},{"name":"R8","value":"0.261727"},{"name":"R9","value":"0.319727"},{"name":"R10","value":"0.320686"},{"name":"R11","value":"0.626901"}]'
OsPSYR2leaf <- fromJSON(json_stringR2L)

OsPSYR2leaf$value <- as.numeric(OsPSYR2leaf$value)
```


### Root
```{r}
json_stringR2R <- '[{"name":"EN_1","value":"5.03828"},{"name":"EN_2","value":"2.73193"},{"name":"EN_3","value":"0"},{"name":"Med_CTRL","value":"3.33534"},{"name":"X35S_1","value":"10.4487"},{"name":"X35S_2","value":"10.5462"},{"name":"X35S_3","value":"12.6099"},{"name":"MZ_1","value":"7.21243"},{"name":"MZ_2","value":"15.0639"},{"name":"MZ_3","value":"9.33031"},{"name":"V_1","value":"0"},{"name":"V_2","value":"0"},{"name":"V_3","value":"0"},{"name":"MCO_1A","value":"0.706237"},{"name":"MCO_1B","value":"0"},{"name":"MCO_2A","value":"1.39683"},{"name":"MCO_2B","value":"3.93875"}]'
ospsyr2rootJSON <- fromJSON(json_stringR2R)
```

```{r}
OsPSYR2root <- ospsyr2rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSYR2root$value <- as.numeric(OsPSYR2root$value)
```


## OsPSY1	LOC_Os05g40850
### Main Stages 
```{r}
json_string1 <- ''

ospsy1JSON <- fromJSON(json_string1)
```

```{r}
OsPSY1 <- ospsy1JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY1$value <- as.numeric(OsPSY1$value)
```


### Leaf 

```{r}
json_string1L <- ''
OsPSY1leaf <- fromJSON(json_string1L)

OsPSY1leaf$value <- as.numeric(OsPSY1leaf$value)
```


### Root
```{r}
json_string1R <- ''
ospsy1rootJSON <- fromJSON(json_string1R)
```

```{r}
OsPSY1root <- ospsyr1rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY1root$value <- as.numeric(OsPSY1root$value)
```

## OsPSY2	LOC_Os05g40890
### Main Stages 
```{r}
json_string2 <- ''

ospsy2JSON <- fromJSON(json_string2)
```

```{r}
OsPSY2 <- ospsy2JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY2$value <- as.numeric(OsPSY2$value)
```


### Leaf 

```{r}
json_string2L <- ''
OsPSY2leaf <- fromJSON(json_string2L)

OsPSY2leaf$value <- as.numeric(OsPSY2leaf$value)
```


### Root
```{r}
json_string2R <- ''
ospsy2rootJSON <- fromJSON(json_string2R)
```

```{r}
OsPSY2root <- ospsyr2rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY2root$value <- as.numeric(OsPSY2root$value)
```


## OsPSY3	LOC_Os01g16980
### Main Stages 
```{r}
json_string3 <- ''

ospsy3JSON <- fromJSON(json_string3)
```

```{r}
OsPSY3 <- ospsy3JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY3$value <- as.numeric(OsPSY3$value)
```


### Leaf 

```{r}
json_string3L <- ''
OsPSY3leaf <- fromJSON(json_string3L)

OsPSY3leaf$value <- as.numeric(OsPSY3leaf$value)
```


### Root
```{r}
json_string3R <- ''
ospsy3rootJSON <- fromJSON(json_string3R)
```

```{r}
OsPSY3root <- ospsyr3rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY3root$value <- as.numeric(OsPSY3root$value)
```


## OsPSY4	LOC_Os01g59970
### Main Stages 
```{r}
json_string4 <- '[{"name":"Seedling_Root_Rep1","value":"1896.65"},{"name":"Seedling_Root_Rep2","value":"1844.54"},{"name":"Seedling_Root_Rep3","value":"1916.31"},{"name":"MatureLeaf_Rep1","value":"1375.48"},{"name":"MatureLeaf_Rep2","value":"1321.41"},{"name":"MatureLeaf_Rep3","value":"1679.63"},{"name":"YoungLeaf_Rep1","value":"2111.38"},{"name":"YoungLeaf_Rep2","value":"1913.63"},{"name":"YoungLeaf_Rep3","value":"2860.13"},{"name":"SAM_Rep1","value":"669.913"},{"name":"SAM_Rep2","value":"737.604"},{"name":"SAM_Rep3","value":"550.782"},{"name":"YoungInflorescence_Rep1","value":"880.759"},{"name":"YoungInflorescence_Rep2","value":"1064.84"},{"name":"YoungInflorescence_Rep3","value":"1501.67"},{"name":"InflorescenceP2_Rep1","value":"1033.92"},{"name":"InflorescenceP2_Rep2","value":"948.022"},{"name":"InflorescenceP2_Rep3","value":"941.335"},{"name":"InflorescenceP3_Rep1","value":"1035.9"},{"name":"InflorescenceP3_Rep2","value":"1364.78"},{"name":"InflorescenceP3_Rep3","value":"1295.84"},{"name":"InflorescenceP4_Rep1","value":"1324.48"},{"name":"InflorescenceP4_Rep2","value":"1457.69"},{"name":"InflorescenceP4_Rep3","value":"1280.95"},{"name":"InflorescenceP5_Rep1","value":"1089.39"},{"name":"InflorescenceP5_Rep2","value":"1451.68"},{"name":"InflorescenceP5_Rep3","value":"1324.47"},{"name":"InflorescenceP6_Rep1","value":"2376.01"},{"name":"InflorescenceP6_Rep2","value":"2670.33"},{"name":"InflorescenceP6_Rep3","value":"2839.44"},{"name":"Seed_S1_Rep1","value":"1980.76"},{"name":"Seed_S1_Rep2","value":"1972.66"},{"name":"Seed_S1_Rep3","value":"2391.39"},{"name":"Seed_S2_Rep1","value":"1459.54"},{"name":"Seed_S2_Rep2","value":"1620.12"},{"name":"Seed_S2_Rep3","value":"1530.8"},{"name":"Seed_S3_Rep1","value":"1690.4"},{"name":"Seed_S3_Rep2","value":"1531.55"},{"name":"Seed_S3_Rep3","value":"1577.77"},{"name":"Seed_S4_Rep1","value":"1912.15"},{"name":"Seed_S4_Rep2","value":"1894.71"},{"name":"Seed_S4_Rep3","value":"2120.19"},{"name":"Seed_S5_Rep1","value":"2417.35"},{"name":"Seed_S5_Rep2","value":"2661.34"},{"name":"Seed_S5_Rep3","value":"3032.98"}, {"name":"Stigma_Rep1","value":"817.987"},{"name":"Stigma_Rep2","value":"964.226"},{"name":"Stigma_Rep3","value":"953.361"},{"name":"Ovary_Rep1","value":"572.141"},{"name":"Ovary_Rep2","value":"608.633"},{"name":"Ovary_Rep3","value":"976.123"},{"name":"SuspensionCell_Rep1","value":"166.062"},{"name":"Shoot_Rep1","value":"2391.83"},{"name":"Root_Rep1","value":"1656.28"},{"name":"Anther_Rep1","value":"2327.55"},{"name":"Embryo_Rep1","value":"1666.7"},{"name":"Endosperm_Rep1","value":"1326.51"},{"name":"5d-seed_Rep1","value":"1924.93"}, {"name":"Aerobic_coleoptile_Rep1","value":"410.122"},{"name":"Aerobic_coleoptile_Rep2","value":"478.443"},{"name":"Anoxic_coleoptile_Rep1","value":"483.001"},{"name":"Anoxic_coleoptile_Rep2","value":"655.604"} ,{"name":"RICE_CTRL","value":"480.722"}]'
ospsy4JSON <- fromJSON(json_string4)
```


### Leaf 
```{r}
json_string4L <- ''
OsPSY4leaf <- fromJSON(json_string4L)

OsPSY4leaf$value <- as.numeric(OsPSY4leaf$value)
```


### Root
```{r}
json_string4R <- ''
ospsy4rootJSON <- fromJSON(json_string4R)
```

```{r}
OsPSY4root <- ospsyr4rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY4root$value <- as.numeric(OsPSY4root$value)
```


## OsPSY5	LOC_Os11g38790
### Main Stages 
```{r}
json_string5 <- ''

ospsy5JSON <- fromJSON(json_string5)
```

```{r}
OsPSY5 <- ospsy5JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY5$value <- as.numeric(OsPSY5$value)
```


### Leaf 

```{r}
json_string5L <- ''
OsPSY5leaf <- fromJSON(json_string5L)

OsPSY5leaf$value <- as.numeric(OsPSY5leaf$value)
```


### Root
```{r}
json_string5R <- ''
ospsy5rootJSON <- fromJSON(json_string5R)
```

```{r}
OsPSY5root <- ospsyr5rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY5root$value <- as.numeric(OsPSY5root$value)
```


## OsPSY6	LOC_Os07g43770
### Main Stages 
```{r}
json_string6 <- ''

ospsy6JSON <- fromJSON(json_string6)
```

```{r}
OsPSY6 <- ospsy6JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY6$value <- as.numeric(OsPSY6$value)
```


### Leaf 

```{r}
json_string6L <- ''
OsPSY6leaf <- fromJSON(json_string6L)

OsPSY6leaf$value <- as.numeric(OsPSY6leaf$value)
```


### Root
```{r}
json_string6R <- ''
ospsy6rootJSON <- fromJSON(json_string6R)
```

```{r}
OsPSY6root <- ospsyr6rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY6root$value <- as.numeric(OsPSY6root$value)
```


## OsPSY7	LOC_Os05g46470
### Main Stages 
```{r}
json_string7 <- ''

ospsy7JSON <- fromJSON(json_string7)
```

```{r}
OsPSY7 <- ospsy7JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY7$value <- as.numeric(OsPSY7$value)
```


### Leaf 
```{r}
json_string7L <- ''
OsPSY7leaf <- fromJSON(json_string7L)

OsPSY7leaf$value <- as.numeric(OsPSY7leaf$value)
```


### Root
```{r}
json_string7R <- ''
ospsy7rootJSON <- fromJSON(json_string7R)
```

```{r}
OsPSY7root <- ospsyr7rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY7root$value <- as.numeric(OsPSY7root$value)
```


## OsPSY8	LOC_Os01g15970
### Main Stages 
```{r}
json_string8 <- ''

ospsy8JSON <- fromJSON(json_string8)
```

```{r}
OsPSY8 <- ospsy8JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY8$value <- as.numeric(OsPSY8$value)
```


### Leaf 

```{r}
json_string8L <- ''
OsPSY8leaf <- fromJSON(json_string8L)

OsPSY8leaf$value <- as.numeric(OsPSY8leaf$value)
```


### Root
```{r}
json_string8R <- ''
ospsy8rootJSON <- fromJSON(json_string8R)
```

```{r}
OsPSY8root <- ospsyr8rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY8root$value <- as.numeric(OsPSY8root$value)
```


## OsTPST	LOC_Os06g06370
### Main Stages 
```{r}
json_string9 <- ''

ospsy9JSON <- fromJSON(json_string9)
```

```{r}
OsPSY9 <- ospsy9JSON %>% 
    separate(name, into=c("name", "Sample #"), sep="_Rep") 

OsPSY9$value <- as.numeric(OsPSY9$value)
```


### Leaf 

```{r}
json_string9L <- ''
OsPSY9leaf <- fromJSON(json_string9L)

OsPSY9leaf$value <- as.numeric(OsPSY9leaf$value)
```


### Root
```{r}
json_string9R <- ''
ospsy9rootJSON <- fromJSON(json_string9R)
```

```{r}
OsPSY9root <- ospsyr9rootJSON %>% 
  separate(name, into=c("name", "Sample #"), sep="_")

OsPSY9root$value <- as.numeric(OsPSY9root$value)
```


# Combining data







